---
title: LaTeX Blog?
lang: en
---
\usepackage{hyperref}

Markdown is nice for writing blogs, but converting it to PDF can be difficult.
How about writing blogs in LaTeX?
This page is such an attempt.

\subsection{Sections}\label{sec:sections}
Obviously, sections are equivalent to \verb|<h1>| while subsections are \verb|<h2>|.
Referencing sections like (Section \ref{sec:sections}) does not work yet, as of the time of writing.
Of course, it is possible for this example to work in some future time when I fix it.

\subsection{Equations}\label{sec:eqs}

No \LaTeX document (Note the \verb|\LaTeX| command eats a space) is complete without an equation:

\begin{equation}
    \oiint_{\partial\Omega} \mathbf{E} \cdot \mathrm{d}\mathbf{S} = {1\over\epsilon_0}\iiint_\Omega \rho \mathrm{d}V
\end{equation}

Again, labeling does not seem to work.
This is probably related to how I hacked in KaTeX, and that I do not have \verb|pandoc-crossref| enabled yet.

Now, let's try \verb|aligned|:

\begin{aligned}
    \oiint_{\partial\Omega} \mathbf{E} \cdot \mathrm{d}\mathbf{S} &= {1\over\epsilon_0}\iiint_\Omega \rho \mathrm{d}V \\
    \oiint_{\partial\Omega} \mathbf{B} \cdot \mathrm{d}\mathbf{S} &= 0 \\
    \oint_{\partial\Sigma} \mathbf{E} \cdot \mathrm{d}\mathbf{l}
    &= -{\mathrm{d}\over\mathrm{d}t} \iint_\Sigma \mathbf{B} \cdot \mathrm{d}\mathbf{S} \\
    \oint_{\partial\Sigma}\mathbf{B} \cdot \mathrm{d}\mathbf{l}
    &= \mu_0\left(\iint_\Sigma \mathbf{J}\cdot \mathrm{d}\mathbf{S} + \epsilon_0{\mathrm{d}\over\mathrm{d}t}\iint_\Sigma \mathbf{E}\cdot\mathrm{d}\mathbf{S} \right)
\end{aligned}

Obvously, this works.
However, LaTeX seems to be a bit overkill for a blogging environment.
The fine-grain controls on typesetting does not really work after HTML generation, and equations are limited to KaTeX support anyways.

So... I will probably stick to Markdown for this blog.
I know there is Asciidoc which stands between Markdown and LaTeX in the spectrum of free-flow vs structured, but Pandoc cannot read Asciidoc yet.